Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
petit fix
correction exemple

There are many possible combinations of the above techniques, and it is not evident which ones perform more or less precisely or more or less efficiency on real-life examples. One needs to experiment.
Unfortunately, the published literature on the subject lacks experimental comparative assessments. One purpose of this article is therefore to propose such experimental results.

@@

Widening operations have a somewhat counterintuitive behavior: the result of an analysis (postcondition) is not necessarily monotonic with respect to the precondition. For instance, classical interval analysis with widening and decreasing iterations on the following loop yields a loop invariant $x \in [0,+\infty)$ if the precondition is $x \in [0,0]$ , but $x \in [0,10]$ (strictly stronger) if the precondition is $x \in [0,10]$ (strictly weaker):
\lstinline|while (x != 10) x=x+1;|.
This means that, when using widenings, being locally more precise (for instance, by using more expressive abstract domains, or widening operators that climb more slowly \cite{BagnaraHRZ05SCP}) does not necessarily translate into higher final precision.
It is almost always possible to concoct examples where a supposedly more precise abstraction (e.g. polyhedra) yields less precise results than a less precise one (e.g. intervals), but are these examples representative of real programs?
This justifies our recourse to evaluation on realistic examples~(\S~\ref{sec:compare_techniques}).

@@

Widening iterations converge to $\lstinline|x_old| \in (-\infty,+\infty)$; let us now see why decreasing iterations fail to recover the desired invariant.
The \lstinline|x >= x_old+10| test at line~6, if taken, yields $\lstinline|x_old| \in (-\infty,99990)$; followed by \lstinline|x = x_old+10|, we obtain $\lstinline|x| \in (-\infty,\allowbreak 100000]$, and the same after union with the no-operation ``else'' branch. Line~7 yields $\lstinline|x| \in (-\infty,+\infty)$.

We could use ``widening up to'' or ``widening with thresholds'', propagating the ``magic values'' $\pm 100000$ associated to \lstinline|x| into~\lstinline|x_old|, but these syntactic approaches cannot directly cope with programs for which $\lstinline|x|  \in [-100000,+100000]$ is itself obtained by analysis.
The guided static analysis of \citet{DBLP:conf/sas/GopanR07} performs slightly better, and obtains $\verb|x_old| \in (-\infty,100000]$.

>>>>

\MM{Peut-être dire quelque part vers ici que le widening n'est en
  général pas monotone, et que donc on ne peut jamais rien dire en
  théorie sur la précision vu qu'être plus précis à une itération peut
  faire perdre en précision la suivante ...}

There are many possible combinations of the above techniques, and it is not
evident which ones perform more or less precisely or more or less efficiently on real-life examples. One needs to experiment. Unfortunately, the published literature on the subject lacks experimental comparative assessments. One purpose of this article is therefore to propose such experimental results.
\medskip

@@

@@

\JH{$99990)$, ca designe bien une borne d'intervalle ouvert ? J'ai plus
l'habitude a la notation $99990[$}
Widening iterations converge to $\lstinline|x_old| \in (-\infty,+\infty)$; let us now see why decreasing iterations fail to recover the desired invariant.
The \lstinline|x > x_old+10| test at line~6, if taken, yields $\lstinline|x_old|
\in (-\infty,99990)$; followed by \lstinline|x = x_old+10|, we obtain
$\lstinline|x| \in (-\infty,\allowbreak 100000)$, and the same after union with the no-operation ``else'' branch. Line~7 yields $\lstinline|x| \in (-\infty,+\infty)$.

We could use ``widening up to'' or ``widening with thresholds'', propagating the ``magic values'' $\pm 100000$ associated to \lstinline|x| into~\lstinline|x_old|, but these syntactic approaches cannot directly cope with programs for which $\lstinline|x|  \in [-100000,+100000]$ is itself obtained by analysis.
The guided static analysis of \citet{DBLP:conf/sas/GopanR07} does not perform
better, and also obtains $\verb|x_old| \in (-\infty,+\infty)$.
